Bird beak's elaboration and exploration

### 2021-11-23 Analysis/03-elaboration_exploration_analyses.Rmd
Update 03-elaboration_exploration_analyses.Rmd

>>>>

These three analyses will be called respectively **group on phylogeny**, **species on phylogeny** and **species on group** respectively.

TODO: add about projection correction: absolute value - 0.5 (because 1) we're not interested in which direction the elaboration goes and 2) centre of the projection is 0.5 not 0)

```{r}

set.seed(42)
## Space plot
cor_matrix <- matrix(cbind(1, 0.8, 0.8, 1), nrow = 2)
space <- space.maker(10, 2, rnorm, cor.matrix = cor_matrix)
lim <- c(floor(range(space)[1]), ceiling(range(space)[2]))

par(mfrow = c(2, 2))

## Plot 1
plot(space, pch = 19, xlab = "Trait 1", ylab = "Trait 2", xlim = lim, ylim = lim, col = "black", main = "Original space")

## Plotting the ellipse
lines(ellipse::ellipse(cor_matrix, level = 0.75), col = "blue", lwd = 1)

## Plotting the major axis
lines(get.one.axis(list(VCV = cor_matrix, Sol = c(0,0)), level = 0.75), lwd = 3, col = "blue", lty = 1)

## Plotting a phylogenetic major axis
lines(x = c(-1.2, 2), y = c(0, 0.75), lwd = 3, col = "orange")

legend("topleft", pch = c(19, NA, NA, NA), lty = c(NA, 1,1,1), lwd = c(NA, 1, 3, 3), legend = c("Group of species", "95% CI ellipse for the group", "Major axis for the group", "Major axis for the phylogeny"), col = c("black", "blue", "blue", "orange"))

## Translate the major axis

plot(space, pch = 19, xlab = "Trait 1", ylab = "Trait 2", xlim = lim, ylim = lim, col = "grey", main = "Group on phylogeny")

## Plotting the ellipse
lines(ellipse::ellipse(cor_matrix, level = 0.75), col = "grey", lwd = 1)

## Plotting the major axis
lines(get.one.axis(list(VCV = cor_matrix, Sol = c(0,0)), level = 0.75), lwd = 3, col = "grey", lty = 1)

## Plotting a phylogenetic major axis
lines(x = c(-1.2, 2), y = c(0, 0.75), lwd = 3, col = "orange")

## Translating the axis

plot(2, main = "species on phylogeny")
plot(3, main = "species on group")
```
